Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-02-03 RR_manuscript/Draft_RR.Rmd
:bug: - fix bug on RR code

```{r funnel-calc, include=FALSE, eval=FALSE}
# meta_bm is the meta-analytical Bayesian regression model
meta_bm_est <- fixef(meta_bm)["Intercept","Estimate"
meta_bm_q2.5 <- fixef(meta_bm)["Intercept","Q2.5"]
meta_bm_q97.5 <- fixef(meta_bm)["Intercept","Q97.5"]

>>>>

```{r funnel-calc, include=FALSE, eval=FALSE}
# meta_bm is the meta-analytical Bayesian regression model
meta_bm_est <- fixef(meta_bm)["Intercept","Estimate"]
meta_bm_q2.5 <- fixef(meta_bm)["Intercept","Q2.5"]
meta_bm_q97.5 <- fixef(meta_bm)["Intercept","Q97.5"]
